---
title: "Weight of Fish"
author: "Jonathan Paul P. Clavio"
date: "November 3 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv("Fish.csv",header=TRUE)
```






# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We are using numerical~numerical since our two variables we are looking at are all numerical explanatory variables.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
Fishies=filter(Fishdata, Species == "Perch")
Fishies = select(Fishies,-Species)
pairs(Fishies)
```


#### Best variables with Perch is Height~Width.  


```{r}
FishiesB=filter(Fishdata, Species == "Bream")
FishiesB = select(FishiesB,-Species)
pairs(FishiesB)
```


#### The best variables for Bream fishes is Length2~Height  

```{r}
FishiesS=filter(Fishdata, Species == "Smelt")
FishiesS = select(FishiesS,-Species)
pairs(FishiesS)
```


#### The best 2 variables for Smelt is Weight~L2.  

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
summary(Fishies)
```


```{r}
summary(FishiesB)
```

```{r}
summary(FishiesS)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


#### The best is Height and Width for Perch.  


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


#### The best variables for Bream to find weight is Length2 and Height.  

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


#### The best to variables is Length2 and Width.  
 
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
Perchmodel=lm(Weight~Height+Width,data=Fishies)
summary(Perchmodel)
```

#### Adjusted R-Squared for Perch is 0.94.    

```{r}
Breammodel=lm(Weight~Length2+Height,data=FishiesB)
summary(Breammodel)
```

#### Adjusted R-square for Bream fishes is 0.9356.  


```{r}
Smeltmodel=lm(Weight~Length2+Width,data=FishiesS)
summary(Smeltmodel)
```

#### Adjusted R-squared for Smelt is 0.9645.  


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

To predict the weight of fishes (Perch,Bream, and Smelt), we found two variables in each fishes that has a correlation of the two variables and the weight it may be at.  
For Perch, we used the two variables Height and Width to predict weight. The Adjusted variable is 0.94 also.  
For Bream and Smelt we used the same variable "Length2" and used Height and Width respectively. The Adjusted variable for Bream was 0.9356 and for Smelt was 0.9645.  
With this we found that the different fishes may use 1 of the same variables but more likely each fish uses their unique variable combinations to allow us to predict weight.  